\vspace{-2em}The 4th Workshop on Sustainable Software for Science: Best Practices and Experiences (WSSSPE4)

### 2016-06-11 WSSSPE4_proposal/WSSSPE4_proposal.tex
re-enabled page numbers
adding to assessment

\pagestyle{empty}

@@

Reports describing the activities of WSSSPE and WSSSPE2 culminated in peer-reviewed articles~\cite{WSSSPE1,WSSSPE2}, while the report from WSSSPE3 is currently undergoing peer review (and is available via the arXiv)~\cite{WSSSPE3}; all reports are publicly available via publication in an open-access journal.
A similar report will be prepared at the conclusion of WSSSPE4, and following the practices of past workshops will be written collaboratively and openly on GitHub.

@@

>>>>

%\pagestyle{empty}

@@

Reports describing the activities of WSSSPE and WSSSPE2 culminated in peer-reviewed articles~\cite{WSSSPE1,WSSSPE2}, while the report from WSSSPE3 is currently undergoing peer review (and is available via arXiv)~\cite{WSSSPE3}; all reports are publicly available via publication in an open-access journal.
A similar report will be prepared at the conclusion of WSSSPE4, and following the practices of past workshops will be written collaboratively and openly on GitHub.

@@

\textcolor{red}{How will we know if this is successful? - for track 2, survey attendees?  for track 1, see if we have proposals submitted or activities underway six months later?}
